### 2018-01-16 Documents/bootcamp_syllabus.tex
Syllabus updates

>>>>

Sometimes you want to know more. Below are two resources that I find quite useful:
\begin{itemize}
\item \href{https://www.amazon.com/Python-Data-Analysis-Wrangling-IPython/dp/1491957662/}{Python for Data Analysis (2nd Edition)}, by Wes Mckinney. Definitive guide to Python for data science and scientific computation, by the creator of Pandas.
\item \href{https://www.amazon.com/Python-Data-Science-Handbook-Essential/dp/1491912057/}{Python Data Science Handbook}, by Jake VanderPlas. Very similar focus as above, extensive chapter on Machine Learning. Great GitHub repository with lots of nice, worked out notebooks.
\end{itemize}
